Learning CNN filters from user-drawn image markers for coconut-tree image classification

### 2020-07-23 main.tex
professor's changes

A well-trained CNN model should detect image regions that best discriminate classes as positive activations, improve class separation by eliminating negative activations, and aggregate the resulting activations locally (pooling) and globally (flattening) into a highly dimensional and sparse feature space, in which a linear classifier should separate the classes with reasonable success. Nevertheless, it is common to assume that the classes are piecewise linearly separable and apply fully connected layers -- a Multi-Layer Perceptron (MLP) classifier -- for feature space reduction and classification. The training of a CNN usually relies on weight optimization using backpropagation, which requires a higher number of annotated images as deep as the model is. In FLIM, we eliminate the need for backpropagation to train convolutional layers by finding a set ${\cal F}$ of filters that can detect discriminant regions from all classes.

@@

We used a dataset from~\cite{8899005}, which contains regions of aerial images with and without coconut trees from the Kingdom of Tonga, as acquired in October 2017~\footnote{The images are available in \url{blog.werobotics.org/2018/01/11/open-ai-challenge-2}.}. Each region should be classified as containing one or none coconut tree, but part of coconut trees from adjacent regions might appears near the region's border. The Humanitarian OpenStreetMap community annotated the regions. The dataset consists of 13587 regions with $90 \times 90$ pixels with resolution under $10$\si{\square\centi\metre}, being 10268 and 3319 regions annotated as containing and not containing coconut trees, respectively. We converted the region images to the LAB color space, with each channel normalized within $[0,1]$.

To assess the impact of FLIM in reducing the need for annotated samples, we randomly selected 100 regions from each class for training and left the remaining 11387 regions for testing. We repeated this procedure three times to compute the mean and the standard deviation of the results in precision, recall, and f-score. By vectorizing and projecting the 200 training images of each split on 2D with t-SNE~\cite{maaten2008visualizing}, we identified cohesive groups of images from each class and selected two representative images from each class to draw markers.  The selected images from one split can be seen in Figure \ref{fig:markers}. We placed markers on these images in regions that we thought to better distinguish between coconut and non-coconut classes.

>>>>

\textcolor{red}{A well-trained CNN model should detect image regions that best discriminate classes as positive activations, improve class separation by eliminating negative activations, and aggregate the resulting activations locally (pooling) and globally (flattening) into a highly dimensional and sparse feature space, in which a linear classifier should separate the classes with reasonable success.} Nevertheless, it is common to assume that the classes are piecewise linearly separable and apply fully connected layers -- a Multi-Layer Perceptron (MLP) classifier -- for feature space reduction and classification. The training of a CNN usually relies on weight optimization using backpropagation, which requires a higher number of annotated images as deep as the model is. In FLIM, we eliminate the need for backpropagation to train convolutional layers by finding a set ${\cal F}$ of filters that can detect discriminant regions from all classes.

@@

We used a dataset from~\cite{8899005}, which contains regions of aerial images with and without coconut trees from the Kingdom of Tonga, as acquired in October 2017~\footnote{The images are available in \url{blog.werobotics.org/2018/01/11/open-ai-challenge-2}.}. Each region should be classified as containing one or none coconut tree, but part of coconut trees from adjacent regions might appears near the region's border. The Humanitarian OpenStreetMap community annotated the regions. The dataset consists of 13587 regions with $90 \times 90$ pixels \textcolor{red}{with resolution under $10$\si{\square\centi\metre}}, being 10268 and 3319 regions annotated as containing and not containing coconut trees, respectively. We converted the region images to the \textcolor{red}{LAB color space}, with each channel normalized within $[0,1]$.

To assess the impact of FLIM in reducing the need for annotated samples, we randomly selected 100 regions from each class for training and left \textcolor{red}{the remaining 11387 regions} for testing. \textcolor{red}{We repeated this procedure three times to compute the mean and the standard deviation of the results in precision, recall, and f-score.} By vectorizing and projecting the 200 training images of each split on 2D with t-SNE~\cite{maaten2008visualizing}, \textcolor{red}{we identified cohesive groups of images from each class and selected two representative images from each class to draw markers.}  The selected images from one split can be seen in Figure \ref{fig:markers}. We placed markers on these images in regions that we thought to better distinguish between coconut and non-coconut classes.
